%Two resources useful for abstract writing.
% Guidance of how to write an abstract/summary provided by Nature: https://cbs.umn.edu/sites/cbs.umn.edu/files/public/downloads/Annotated_Nature_abstract.pdf %https://writingcenter.gmu.edu/guides/writing-an-abstract
\chapter*{\center \Large  Abstract}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% Replace all text with your text
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
Tank Tactics is an engaging online multiplayer tank battle game developed using the Unity game engine and its multiplayer technologies, including the Netcode for GameObjects (NGO) framework and Unity Gaming Services (UGS) Relay \& Lobby. The project aimed to provide an enjoyable and accessible multiplayer experience for up to 20 players simultaneously, addressing the common challenges of traditional online games, such as the need for manual port forwarding and IP address sharing.
\\
\noindent
\\
Through an extensive literature review, the research explored the history of multiplayer gaming, tracing its evolution from early electronic games to the rise of modern online multiplayer experiences. It examined the challenges faced by developers in creating online multiplayer games, including connectivity issues, complex network configurations, scalability, and security concerns. The study investigated various network topologies, such as client-server and peer-to-peer models, leading to the adoption of a client-hosted listen server model for Tank Tactics, balancing the advantages of both architectures.
\\
\noindent
\\
The methodology involved leveraging Unity's powerful game development tools, including its intuitive editor, component-based architecture, and scripting capabilities using C\#. The NGO framework and UGS services were implemented to enable seamless multiplayer connectivity and self-hosting, eliminating the need for manual port forwarding or IP address sharing. The game's core gameplay mechanics, including intuitive tank controls, precise shooting, and a dynamic coin system, were meticulously designed to deliver an engaging and rewarding experience.
\\
\noindent
\\
The results showcased the successful integration of seamless multiplayer connectivity, engaging gameplay mechanics, and advanced features such as a real-time leaderboard, mini-map, healing zones, and bounty coins. Player feedback and survey results validated the effectiveness of the development efforts, demonstrating the game's ability to address initial challenges and deliver an accessible and polished multiplayer experience.
\\
\noindent
\\
The project's findings highlighted the significance of leveraging modern technologies and frameworks to overcome traditional multiplayer game development challenges. The modular and well-structured approach to development ensured maintainability and extensibility, facilitating future expansions and improvements. Potential areas for future work include cross-platform support, advanced matchmaking systems, social features, performance optimization, and monetization strategies.
\\
\noindent
\\
Overall, Tank Tactics exemplified the power and versatility of Unity's multiplayer technologies in creating an accessible and engaging online multiplayer gaming experience.



%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%s
~\\[1cm]
\noindent % Provide your key words
\textbf{Keywords:} Online Multiplayer Game, Unity, Netcode for GameObjects, Unity Gaming Services, Tank Battle, Networking

\vfill
\noindent
\textbf{Report's total word count:} 12402

